KidsAIR initial PM data work

### 2019-12-24 sums_data_cleaning.Rmd
SUMs cleaning

---
title: "KidsAIR initial PM data work"
author: "Ethan Walker"
date: "Started 23 Dec 2019, Updated 23 Dec 2019"
output: pdf_document
---

@@

```{r}
wmt_sums_data_log <- read_csv("Input/WMT/wmt_sums_data_log.csv") %>% 
  mutate(home_winter_id = as.character(HomeWinterID),
         date = ChangeDate,
         time = ChangeTime,
         alarms = Alarms,
         file_name = ibutFile,
         notes = `REPLACE(REPLACE(Notes`) %>% 
  select(home_winter_id, date, time, alarms, file_name, notes)

kids_linked_ids <- read_rds("Output/kids_linked_ids.rds") %>% 
  filter(area == "WMT") %>% 
  select(home_winter_id, home)

wmt_sums_log <- wmt_sums_data_log %>% 
  left_join(kids_linked_ids, by = "home_winter_id") %>% 
  select(home_winter_id, home, date, time, alarms, file_name, notes)

>>>>

---
title: "KidsAIR initial PM data work"
author: "Ethan Walker"
date: "Started 23 Dec 2019, Updated 24 Dec 2019"
output: pdf_document
---

@@

```{r}
wmt_sums_data_log <- read_csv("Input/WMT/wmt_sums_data_log_updated.csv") %>% 
  mutate(home_winter_id = as.character(HomeWinterID),
         date = ChangeDate,
         time = ChangeTime,
         alarms = Alarms,
         file_name = ibutFile,
         notes = `REPLACE(REPLACE(Notes`) %>% 
  select(home_winter_id, date, time, alarms, file_name, notes)

kids_linked_ids <- read_rds("Output/kids_linked_ids.rds") %>% 
  filter(area == "WMT") %>% 
  select(home_winter_id, home, home_id)

wmt_sums_log <- wmt_sums_data_log %>% 
  left_join(kids_linked_ids, by = "home_winter_id") %>% 
  select(home_winter_id, home, home_id, date, time, alarms, file_name, notes)
